Democracy, Public Support, and Measurement Uncertainty

### 2021-05-03 paper/dcpo_demsupport.Rmd
cls uncertain

@@

```{r claassenUncertaintyAJPS}
claassen_replication <- read_csv(here::here("data", "claassen_replication.csv"),
                   col_types = "cdcddcdc") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

# length(unique(claassen_replication$country))
# 
# ls_country <- unique(claassen_replication_input$data$country)
# first_year <- min(claassen_replication_input$data$year)

@@

df_result_clsUncertain <- map(mod_ls, estimate_cls)

save(df_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

>>>>

names(tidy_result_cls) <- names(glance_result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

@@

```{r claassenUncertaintyAJPS}
claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

@@

ls_iv <- c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) ")

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
    )
)

tidy_result_clsUncertain <- map(ls_mod, possibly(function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_vars <- ifelse(class(result[[1]])[1] == "plm", 
                        mitools::MIextract(result, fun = vcovBK_se),
                        mitools::MIextract(result, fun = vcovHC_se))
  result_betas <- mitools::MIextract(result, fun = coef)

  summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))
}, otherwise = NA_real_))

save(tidy_result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```
